\title{Mechanical Conditions in Rotating Disk of General Cross-Section}
\author{} \tocauthor{V. Kotlan} \institute{}
\maketitle
\begin{center}
{\large Ivo Dolezel}\\
University of West Bohemia\\
{\tt idolezel@kte.zcu.cz}
\\ \vspace{4mm}{\large Vaclav Kotlan}\\
University of West Bohemia\\
{\tt vkotlan@kte.zcu.cz}
\\ \vspace{4mm}{\large Pavel Kus}\\
Academy of Sciences of the Czech Republic\\
{\tt pavel.kus@gmail.com}
\\ \vspace{4mm}{\large Bohus Ulrych}\\
University of West Bohemia\\
{\tt ulrych@kte.zcu.cz}

\end{center}

\section*{Abstract}

Numerous technical applications work with disks of general cross sections pressed or freely put on shafts and rotating at high revolutions \cite{skopek}, \cite{kim}. We can mention, for example, active wheels of gas or steam turbines and axial compressors, rotors of centrifugal separators, fly-wheels realized either as stabilizers of various mechanical systems or as high-revolution superconductive accumulators of energy and so forth. The paper deals with the determination of the mechanical situation (stresses and displacements) in such devices, whose knowledge will be later used for overall evaluation of properties of shrink fits disk-shaft prepared by means of induction heating. This kind of problem should be solved like contact problem. Authors present an iterative procedure of its solution. After presenting the technical formulation of the problem, it is described by an appropriate mathematical model given by the Lamé equation supplemented with correct boundary conditions \cite{pantelyat}. This model is then repeatedly solved numerically by the finite element analysis. The principal part of the paper consists in the discussion of results obtained by the solution of several illustrative examples.


\bibliographystyle{plain}
\begin{thebibliography}{10}

\bibitem{skopek}
{\sc M. Skopek and B. Ulrych and I. Dolezel}. {Optimized regime of induction heating of a disk before its pressing on shaft}. IEEE Trans. Magn., Vol. 37, No. 5, 2001, pp. 3380-3383.



\bibitem{kim}
{\sc J.K. Kim and S.Y. Kwak and S.M. Cho and H.K. Jung and T.K. Chung}. {Optimization of multilayer buried magnet synchronous machine combined with stress and thermal analysis}. IEEE Trans. Magn., Vol. 42, No. 4, 2006, pp. 1023-1026.



\bibitem{pantelyat}
{\sc M. Pantelyat}. {Coupled electromagnetic, thermal and elastic-plastic simulation of multi-impulse inductive heating}. International Journal of Applied Electromagnetics and Mechanics, Vol. 9, No. 1, 1998, pp. 11-24.

\end{thebibliography}
