\title{Multiphysics Challenges and Recent Advances in Composable Solvers}
\author{} \tocauthor{L. C. McInnes} \institute{}
\maketitle
\begin{center}
{\large Lois Curfman McInnes}\\
Mathematics and Computer Science Division\\
Argonne National Laboratory\\
{\tt curfman@mcs.anl.gov}

\end{center}

\section*{Abstract}

Multimodel and multiphysics applications are of increasing interest as computational science communities strive to address broad questions about complex physical and engineered systems characterized by multiple, interacting physical processes that have traditionally been considered separately.  Large-scale multiphysics simulations can
naturally exploit unprecedented levels of parallelism of emerging extreme-scale architectures. However, much multidisciplinary research is needed to develop efficient, robust, and stable algorithms as well as flexible software for coupled, multiphysics simulations on extreme-scale machines.

This presentation will highlight some challenges and opportunities in multiphysics simulations, as identified during a workshop sponsored by the Institute for Computing in Science in summer 2011 (see https://sites.google.com/site/icismultiphysics2011/).

We will also discuss recent advances in the Portable, Extensible Toolkit for Scientific computing (PETSc) that enable application scientists to investigate composable linear, nonlinear, and timestepping solvers for multiphysics and multilevel methods.
Examples of parallel application usage include lithosphere dynamics, subduction and mantle convection, ice sheet dynamics, subsurface
reactive flow, fusion, mesoscale materials modeling, and power networks.


\bibliographystyle{plain}
\begin{thebibliography}{10}

\bibitem{KeyesMcInnesWoodwardEtAl2011}
{\sc D. E. Keyes, L. C. McInnes, C. Woodward, W. D. Gropp, E. Myra, M. Pernice, J. Bell, J. Brown, A. Clo, J. Connors,  E. Constantinescu, D. Estep, K. Evans, C. Farhat, A. Hakim, G. Hammond, G. Hansen, J. Hill, T. Isaac, X. Jiao, K. Jordan, D. Kaushik, E. Kaxiras, A. Koniges, K. Lee, A. Lott, Q. Lu, J. Magerlein, R. Maxwell, M. McCourt, M. Mehl, R. Pawlowski, A. Peters, D. Reynolds, B. Riviere, et al.} {Multiphysics Simulations: Challenges and Opportunities}. Tech. Rep. ANL/MCS-TM-321, Argonne National Laboratory, Report of workshop sponsored by the Institute for Computing in Science (ICiS), July 30 - Aug. 6, 2011, Park City, Utah (Dec. 2011), see http://www.ipd.anl.gov/anlpubs/2012/01/72183.pdf.



\bibitem{SmithMcInnesConstantinescuEtAl2011}
{\sc B. Smith, L.C. McInnes, E. Constantinescu, M. Adams, S. Balay, J. Brown, M. Knepley, H. Zhang}. {PETSc's Software Strategy for the Design Space of Composable Extreme-Scale Solvers}. Preprint ANL/MCS-P2059-0312, Argonne National Laboratory, see http://www.mcs.anl.gov/uploads/cels/papers/P2059-0312.pdf.

\end{thebibliography}
