\title{Magnetohydrodynamics Propulsion System Mathematical Models, Analysis and Simulation}
\tocauthor{A. Mussa} \author{} \institute{}
\maketitle
\begin{center}
{\large Ali  Mussa}\\
National Program for Aeronautical Technology, King Abdulaziz City for Science and Technology (KACST)\\
{\tt almussa@kacst.edu.sa}

\end{center}

\section*{Abstract}

In this paper we study some techniques for the solution of a complex case of MHD propulsion thruster problems. We present different approaches and investigate such problems proposing utmost promising and innovative methods, techniques and approaches. We furnish a construction of a new MHD convection and magnetoconvection force theory strategic solution technique and concept. Different theoretical and computational aspects are presented. The auxiliary variational inequality as well as the projection method is proposed. Asymptotic analysis for the solution of some more complicated and non-linear MHD as well as MHD turbulence and thruster problems is discussed. We also suggest some variational formulation extension for a similar class of mathematical and engineering problems.


Key Words:  MHD, magnetoconvection, propulsion, thruster, variational inequalities, marginal turbulence.



\bibliographystyle{plain}
\begin{thebibliography}{10}

\bibitem{BibTeX}
{\sc  Mussa and A. I.}. {MHD Plasma: Spherical Region Model-Analytical and Numerical Investigation}. "J. Forshungszentrum Junze in der Helmholtz-Gemeinschaft,  34 (2004), 279-282".

\end{thebibliography}
