\title{Stochastic Methods for Particle Populations in Flows}
\tocauthor{R. Patterson} \author{} \institute{}
\maketitle
\begin{center}
{\large Robert Patterson}\\
Weierstrass Institute\\
{\tt Robert.Patterson@wias-berlin.de}

\end{center}

\section*{Abstract}

Particle formation and growth in flows has a wide range of physical and
engineering applications, from combustion synthesis of nano-particles
to soot formation and from ice and water precipitation in clouds to
pharmaceutical crystallisation.  A range numerical methods
exist for solving population balance equations in these settings.
These include moment methods \cite{Frenklach,Marchisio}, sectional
and finite volume
methods \cite{Kumar} and finite element methods such as \cite{John}.
For simple particle models, these and other methods are very successful,
but they suffer from the `curse of dimensionality' when considering
complex particle models in which particles have many internal coordinates.
In the case of detailed physical models stochastic particle methods
offer a practical way forward that is not limited by model dimension
\cite{Sander}.

The development of stochastic particle methods for population balance
problems describing particle formation has been carried out in the
spatially homogeneous setting \cite{Wagner}.  Extension to spatially
resolved problems with advection is computationally practical, but
numerical tests show that only newer statistically weighted particle
methods \cite{Pat11} provide satisfactory results.  We will provide
some illustrations of what can go wrong; discuss the underlying causes
and demonstrate the application of the method to a problem from
combustion science.

\bibliographystyle{plain}
\begin{thebibliography}{10}

\bibitem{Frenklach}
{\sc M. Frenklach}. {Method of moments with interpolative closure}. Chem. Eng. Sci. 57 (2002) 2229-2239.



\bibitem{Marchisio}
{\sc D. L. Marchisio and R. O. Fox}. {Solution of population balance equations using the direct quadrature method of moments}. J. Aerosol Sci. 36 (2005) 43-73.



\bibitem{Kumar}
{\sc J. Kumar and G. Warnecke and M. Peglow and S. Heinrich}. {Comparison of numerical methods for solving population balance equations incorporating aggregation and breakage}. Powder Tech. 189 (2009) 218-229.



\bibitem{John}
{\sc W. Hackbusch and V. John and A. Khachatryan and C. Suciu}. {A numerical method for the simulation of an aggregation-driven population balance system}. Int. J. Numer. Meth. Fluids, in press, doi:10.1002/fld.2656.



\bibitem{Sander}
{\sc M. Sander and R. I. A. Patterson and A. Braumann and A. Raj and M. Kraft}. {Developing the PAH-PP soot particle model using process informatics and uncertainty propagation}. Proc. Combust. Inst 33 (2011) 675-683.



\bibitem{Wagner}
{\sc A. Eibeck and W. Wagner}. {Stochastic interacting particle systems and nonlinear kinetic equations}. Ann. Appl. Prob. 13 (2003) 845-889.



\bibitem{Pat11}
{\sc R. I. A. Patterson and W. Wagner and M. Kraft}. {Stochastic weighted particle methods for population balance equations}. J Comput. Phys. 230 (2011) 7456-7472.

\end{thebibliography}
