\title{Using Butcher's Tables in Transient PDE Solvers}
\tocauthor{P. Solin} \author{} \institute{}
\maketitle
\begin{center}
{\large \underline{Pavel Solin}}\\
University of Nevada, Reno\\
{\tt solin@unr.edu}
\\ \vspace{4mm}{\large Lukas Korous}\\
FEMhub Inc.\\
{\tt lukas@femhub.com}

\end{center}

\section*{Abstract}

We present a new class of adaptivity algorithms for time-dependent partial differential 
equations (PDE) that combine adaptive higher-order finite elements ($hp$-FEM) in space with 
arbitrary (embedded, higher-order, implicit) Runge-Kutta methods in time. Weak formulation 
is only created for the stationary residual, and the Runge-Kutta
methods are specified via their Butcher's tables. Around 30 Butcher's 
tables for various Runge-Kutta methods with numerically verified 
orders of local and global truncation errors are provided. A time-dependent benchmark 
problem with known exact solution that contains a sharp moving front 
is introduced, and it is used to compare the quality of seven embedded implicit higher-order Runge-Kutta 
methods. Numerical experiments also include a comparison of adaptive low-order FEM and 
$hp$-FEM with dynamically changing meshes. All numerical results presented in this paper 
were obtained using the open source library Hermes (http://hpfem.org/hermes) and they are
reproducible in the Networked Computing Laboratory (NCLab) at http://nclab.com. 

\bibliographystyle{plain}
\begin{thebibliography}{10}

\bibitem{ref1}
{\sc J. C. Butcher}. {Numerical Methods for Ordinary Differential Equations}. J. Wiley \& Sons, 2003.



\bibitem{ref2}
{\sc P. Solin and L. Korous}. {Adaptive Higher-Order Finite Element Methods for Transient PDE Problems Based on }. Journal of Computational Physics, Volume 231, Issue 4, 20 February 2012, pp. 1635-1649.



\bibitem{ref3}
{\sc P. Solin. K. Segeth and I. Dolezel}. {Higher-Order Finite Element Methods}. CRC Press, 2004.

\end{thebibliography}
