\title{Multilevel Monte Carlo Methods and Applications to Uncertainty Quantification in Subsurface flow}
\tocauthor{E. Ullmann} \author{} \institute{}
\maketitle
\begin{center}
{\large Elisabeth  Ullmann}\\
University of Bath\\
{\tt E.Ullmann@bath.ac.uk}

\end{center}

\section*{Abstract}

The efficient quantification of uncertainties in the simulation of subsurface flows plays an important role in many applications such as radioactive waste disposal. The coefficients in such problems are highly uncertain, rough and oscillatory, resulting in very computing-intensive simulations that reach the limits of all existing methods even on the largest supercomputers. To overcome these limits we employ multilevel Monte Carlo (MLMC) \cite{BSZ:2011}, \cite{CGS:2011}, a novel variance reduction technique for standard Monte Carlo simulations. We outline the principles of MLMC and demonstrate the significant gains with respect to standard Monte Carlo for problems arising in groundwater flow.\\

\noindent This is joint work with Andrew Cliffe (Uni Nottingham), Mike Giles (Uni Oxford), Minho Park (Uni Nottingham), Robert Scheichl (Uni Bath) and Aretha Teckentrup (Uni Bath).


\bibliographystyle{plain}
\begin{thebibliography}{10}

\bibitem{BSZ:2011}
{\sc A. Barth and Ch. Schwab and N. Zollinger}. {Multi-level Monte Carlo Finite Element method for elliptic PDEs with stochastic coefficients}. Numer. Math. 11 (2011) 123-161.



\bibitem{CGS:2011}
{\sc K.A.Cliffe  and M.B. Giles and R. Scheichl and A.L. Teckentrup}. {Multilevel Monte Carlo Methods and Applications to Elliptic PDEs with Random Coefficients}. Comp. Vis. Sci. 14 (2011) 3-15.

\end{thebibliography}
