\title{Calibration of FEM Based Computational Model For Thermoelastic Actuator}
\author{} \tocauthor{L. Voracek}\institute{}
\maketitle
\begin{center}
{\large Lukas Voracek}\\
University of West Bohemia\\
{\tt lvoracek@kte.zcu.cz}
\\ \vspace{4mm}{\large Vaclav Kotlan}\\
University of West Bohemia\\
{\tt vkotlan@kte.zcu.cz}

\end{center}

\section*{Abstract}

Setting of position in technical practice may be realized by a number of ways derived from numerous mechanical, hydraulic, pneumatic, electromagnetic and other principles. The main disadvantage of all these systems consists in the presence of movable parts (screws, plungers, etc.) whose movement may negatively affects the available accuracy of such devices.

In previous papers (see, for example \cite{actuator-1}) the authors proposed a purely thermoelastic actuator that worked sufficiently accurately without any movable parts, but only with extremely small shifts ($10^{-5} - 10^{-3}$ m). Possibilities of applications of such actuators, therefore, suffered from rather high setting limitations.

The next papers presented a novel actuator combining a classical electromagnetic device of this kind with thermoelasticity. The device allows accurate setting of position in a wide range of distances (see, for expample \cite{actuator-2}).

This paper is focused more on comparission between the results from numerical model and measurement on the real prototype of thermoelastic actuator. The numerical model is based on FEM computational program Agros2D (program based on Hermes library developed in Pilsen) completed by own scripts in Python. The get results are compared with measurements data from build model of thermolastic actuator. In the theses are discussed the reasons of disagreement and are found possible solutions of their elimination. 



\bibliographystyle{plain}
\begin{thebibliography}{10}

\bibitem{actuator-1}
{\sc I. Dolezel and V. Kotlan and E. Kronerova and B. Ulrych}. {Induction thermoelastic actuator with controllable operation regime}. Compel, Vol. 29, No. 4, 2010, ISSN 0332-1649, p. 1004-1014.



\bibitem{actuator-2}
{\sc I. Dolezel and B. Ulrych and V. Kotlan}. {Combined Actuator for Accurate Setting of Position Based on Thermoelasticity Produced by Induction Heating}. IEEE Transaction on Industry Applications, Vol. 47, No. 5, 2011, ISSN 0093-9994, p. 2250-2256.

\end{thebibliography}
