\title{Computationally Challenging Two-Phase Incompressible Flow Problems on Multi-GPU Systems}
\tocauthor{P. Zaspel} \author{} \institute{}
\maketitle
\begin{center}
{\large Michael Griebel}\\
University of Bonn\\
{\tt griebel@ins.uni-bonn.de}
\\ \vspace{4mm}{\large \underline{Peter Zaspel}}\\
University of Bonn\\
{\tt zaspel@ins.uni-bonn.de}

\end{center}

\section*{Abstract}

Scaling multi-GPU codes are a key component for the Exascale generation of
compute clusters. We thus recently implemented a fully multi-GPU-based scientific
CFD solver for two-phase incompressible fluids
\cite{Griebel2010,Zaspel2011submitted}. Consequently, we are now able to perform
highly scaling simulations of the interaction of two fluids like air and water on
large GPU clusters. This kind of simulation is applied in e.g.~the design of
hydraulic constructions or the study of droplet / bubble dynamics.

Our model for incompressible fluids are the three-dimensional
Navier-Stokes equations. Two-phase flows are introduced by the
level-set technique and the continuum surface force approach. We have discretized the system of equations
with Chorin's projection approach and a finite difference method. High-order WENO
schemes are applied for most space discretizations. Time discretizations are done
with the Adams-Bashforth and the Runge-Kutta method of second and third order.
The necessary pressure Poisson equation is iteratively solved with a
Jacobi-preconditioned conjugate gradient solver. The GPU-code is implemented with
CUDA. For the multi-GPU parallelization, we use MPI and a domain decomposition
method.

Based on the widely improved compute performance of our multi-GPU code over our
original CPU code \cite{Croce2009}, we now look into fields of application which
were often strongly limited by compute performance. These fields include, but are not limited to uncertainty
quantification, optimization and inverse problems. 

In our talk, we will briefly describe our model for two-phase flows and outline
some technical details of our multi-GPU parallel implementation. Beside of some
performance benchmark results, we then present preliminary results of our
latest developments in e.g.~uncertainty quantification on GPUs.

\bibliographystyle{plain}
\begin{thebibliography}{10}

\bibitem{Croce2009}
{\sc  R. Croce and M. Griebel and M. A. Schweitzer}. {Numerical simulation of bubble and droplet-deformation by a level set approach with surface tension in three dimensions}.  International Journal for Numerical Methods in Fluids, 62(9):963-993, 2009.



\bibitem{Griebel2010}
{\sc  M. Griebel and P. Zaspel}. {A multi-GPU accelerated solver for the three-dimensional two-phase incompressible Navier-Stokes equations}. Computer Science - Research and Development, 25(12):65-73, May 2010.



\bibitem{Zaspel2011submitted}
{\sc P. Zaspel and M. Griebel.}. {Solving incompressible two-phase flows on massively parallel multi-GPU clusters}. Computers and Fluids, 2011, submitted, INS Preprint no. 1113.

\end{thebibliography}
